Flatiron cleaning

### 2021-12-07 Rmd/rdi analysis.Rmd
Update and remove more precise rdi

<div class = "row">
<div class = "col-md-6">
```{r rdi plots, fig.height=10, fig.height=9}
# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
#   ggplot(aes(x= drugname))+
#   geom_bar()+
#   theme_minimal(base_size = 14)+
#   coord_flip()+
#   facet_wrap(. ~ therapy)
# 
# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
#   ggplot(aes(x= therapy, y= mean_RDI_per_drug))+
#   geom_boxplot()+
#   # ylim(c(-.25, 3.5))+
#   geom_jitter(shape=16)+
#   labs(x = "", caption = "Warning 1 dot = RDI for 1 patient") +
#   theme_minimal(base_size = 14)+
#   facet_wrap(.~ drugname, ncol = 2)
```
</div>

<div class = "col-md-6">
```{r, fig.height=10, fig.height=9}
# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
#   ggplot(aes(x= drugname, fill= RDI_grp))+
#   geom_bar(position = "fill")+
#   theme_minimal(base_size = 14)+
#   coord_flip()+
#   facet_wrap(. ~ therapy)
# 
# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
#   ggplot(aes(x= therapy, y= mean_RDI_per_drug))+
#   # geom_boxplot()+
#   ylim(c(-.25, 2))+
#   geom_jitter(shape=16, aes(color=RDI_grp))+
#   labs(x = "", caption = "Warning 1 dot = RDI for 1 patient") +
#   theme_minimal(base_size = 14) +
#   guides(color=FALSE)+
#   facet_wrap(.~ drugname, ncol = 2)
```
</div>
</div>

@@

### By Population
```{r, fig.width=12, fig.height=20}
# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
#   # filter(linenumber_new == "1") %>%
#   ggplot(aes(x= raceeth, y= mean_RDI_per_drug#, alpha = mean_RDI_per_drug<0.85
#              ))+
#   geom_boxplot(aes(fill = drugname))+
#   ylim(c(0, 2))+
#   scale_colour_discrete()+
#   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug<0.85))+
#   theme_minimal(base_size = 14)+
#   facet_wrap(drugname ~ therapy, ncol = 2, scales = "free")
```

@@

## 1.RDI summary table
Do you want them together in 1 table?

<span style="color:green">**Platin**</span>  
```{r Table summary Platin}
# Treatment & demo
tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(RDI_carbo_neo, RDI_carbo_neo_grp)) %>%
  tbl_summary(
              label = list(RDI_carbo_neo ~ "RDI")) %>%
  bold_labels()

tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(RDI_carbo_adj, RDI_carbo_adj_grp)) %>%
  tbl_summary(
              label = list(RDI_carbo_adj ~ "RDI")) %>%
  bold_labels()

tbl3 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(RDI_carbo_adj, RDI_carbo_adj_grp)) %>%
  tbl_summary(
              label = list(RDI_carbo_adj ~ "RDI")) %>%
  bold_labels()

tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c(
                           "carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery"),
          quiet = TRUE)
```

<span style="color:green">**Taxanes**</span>  
```{r Table summary Taxanes}
tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("RDI" = RDI_pacli_neo, "RDI cat" = RDI_pacli_neo_grp)) %>%
  tbl_summary() %>%
  bold_labels()

tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
  tbl_summary() %>%
  bold_labels()

tbl3 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
  tbl_summary() %>%
  bold_labels()

@@

# tbl5 <- Frontline %>% filter(therapy == "Upfront Chemo" &
#                                dose_dense == 3) %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c("RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
#   tbl_summary() %>%
#   bold_labels()
tbl6 <- Frontline %>% filter(therapy == "Upfront Surgery" &
                               dose_dense == 3) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
  tbl_summary(
              type = list(RDI ~ "continuous")) %>%
  bold_labels()

# tbl7 <- tbl_merge(list(tbl1, tbl3), tab_spanner = c("Overall", "Dose dense 1+3"))
# tbl8 <- tbl_merge(list(tbl2, tbl4))
# tbl9 <- tbl_merge(list(tbl3, tbl6), tab_spanner = c("Overall", "Dose dense 1+3"))

tbl_stack(list(tbl1, tbl2, tbl3, tbl6),
          group_header = c(
                           "paclitaxel Neo/Upfront Chemo", 
                           "paclitaxel Adj/Upfront Chemo",
                           "paclitaxel Adj/Upfront Surgery",
                           "dose dense paclitaxel Adj/Upfront Surgery"),
          quiet = TRUE)
```
<br>

@@

## Univariable
```{r Table 5 HR}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- tbl2 %>%
  select(vitalstatus, RDI_carbo_neo, RDI_carbo_neo_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- tbl2 %>%
  select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- tbl3 %>%
  select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- tbl2 %>%
  select(vitalstatus, RDI_pacli_neo, RDI_pacli_neo_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- tbl2 %>%
  select(vitalstatus, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- tbl3 %>%
  select(vitalstatus, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel/Upfront Chemo", 
                           "paclitaxel/Upfront Chemo",
                           "paclitaxel/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
In univariable analysis, higher RDI (continuous) of carboplatin in an Adjuvant / Upfront Chemo setting show a worse outcome which is not seen in the categorical variable.  
A trend is observed toward a better survival with higher RDI (continuous) of paclitaxel in an Neoadjuvant / Upfront Chemo. In the contrary, lower RDI (categorical) of paclitaxel in an Adjuvant / Upfront Surgery shows a 51% increase risk of death when underdosed p = 0.091.

@@

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_neo_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel Neo/Upfront Chemo", 
                           "paclitaxel Adj/Upfront Chemo",
                           "paclitaxel Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
In multivariable analysis, categorical RDI for carboplatin or paclitaxel is not a factor associated with survival.

@@

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel Neo/Upfront Chemo", 
                           "paclitaxel Adj/Upfront Chemo",
                           "paclitaxel Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
In multivariable analysis, a higher RDI for carboplatin shows a worse survival (p<0.001) in an Adjuvant / Upfront Chemo setting as seen in the univariable analysis.  
RDI for paclitaxel is not a factor associated with survival.

@@

## Adjusted by other drug
### RDI group
`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat` 
```{r Table 5 HR adjusted rdi group adjusted by other drug}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl2, tbl3),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
When adjusting by each drugs, we observe a 61% increased risk of death for a underdosing of carboplatin in the Neoadjuvant / Upfront Chemo setting (p=0.059) and a 32% increased risk of death for a underdosing of paclitaxel in the Adjuvant / Upfront Surgery setting (p=0.059).

@@

# V.More precise RDI

As you saw, we have a big spread of RDI (it is more complicated than < or > 0.85) so I thought I could make more than 2 groups to compare patients who have a correct RDI, being underdosed or overdosed

>>>>

<div class = "row">
<div class = "col-md-6">
```{r rdi plots, fig.height=10, fig.height=9}
Frontline %>% 
  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
  filter(!is.na(value)) %>% 
  ggplot(aes(x= name))+
  geom_bar(aes(fill = therapy), position = position_dodge(preserve = "single"))+
  theme_minimal(base_size = 14)+
  coord_flip()
  # facet_wrap(. ~ therapy)

Frontline %>% 
  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
  filter(!is.na(value)) %>% 
  ggplot(aes(x= name, y= value))+
  geom_boxplot()+
  # ylim(c(-.25, 3.5))+
  geom_jitter(shape=16)+
  labs(x = "", caption = "Warning 1 dot = RDI for 1 patient") +
  theme_minimal(base_size = 14)+
  coord_flip()+
  facet_wrap(.~ therapy, ncol = 2)
```
</div>

<div class = "col-md-6">
```{r, fig.height=10, fig.height=9}
# Frontline %>% 
#   select(patientid, RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj,
#          RDI_carbo_neo_grp, RDI_pacli_neo_grp, RDI_carbo_adj_grp, RDI_pacli_adj_grp) %>% 
#   pivot_longer(cols = -patientid, names_to = c("RDI", "group"), names_prefix = "_grp")
#   filter(!is.na(value)) %>% 
#   ggplot(aes(x= name))+
#   geom_bar(aes(fill = therapy, alpha = RDI_grp), position = position_dodge(preserve = "single"))+
#   theme_minimal(base_size = 14)+
  # coord_flip()
# 
# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
#   ggplot(aes(x= therapy, y= mean_RDI_per_drug))+
#   # geom_boxplot()+
#   ylim(c(-.25, 2))+
#   geom_jitter(shape=16, aes(color=RDI_grp))+
#   labs(x = "", caption = "Warning 1 dot = RDI for 1 patient") +
#   theme_minimal(base_size = 14) +
#   guides(color=FALSE)+
#   facet_wrap(.~ drugname, ncol = 2)
```
</div>
</div>

@@

### By Population
```{r, fig.width=12, fig.height=20}
Frontline %>% 
  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
  filter(!is.na(value)) %>% 
  ggplot(aes(x= raceeth))+
  geom_bar(aes(fill = therapy), position = position_dodge(preserve = "single"))+
  theme_minimal(base_size = 14)+
  coord_flip()+
  facet_wrap(name ~ ., ncol = 1, scales = "free")
```

@@

## 1.RDI summary table

<span style="color:green">**RDI summary table**</span>  
```{r Table summary Platin}
# Treatment & demo
tbl1 <- Frontline %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("RDI (continous)" = RDI_carbo_neo, "RDI (categorical)" = RDI_carbo_neo_grp, therapy)) %>%
  tbl_summary(by = therapy) %>% 
  bold_labels()

tbl2 <- Frontline %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("RDI (continous)" = RDI_carbo_adj, "RDI (categorical)" = RDI_carbo_adj_grp, therapy)) %>%
  tbl_summary(by = therapy) %>%
  bold_labels()

tbl3 <- Frontline %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("RDI (continous)" = RDI_pacli_neo, "RDI (categorical)" = RDI_pacli_neo_grp, therapy)) %>%
  tbl_summary(by = therapy
              ) %>%
  bold_labels()

tbl4 <- Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("RDI (continous)" = RDI_pacli_adj, "RDI (categorical)" = RDI_pacli_adj_grp, therapy)) %>%
  tbl_summary(by = therapy
              ) %>%
  bold_labels()
tbl5 <- Frontline %>% filter(dose_dense == 3) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("RDI (continous)" = RDI_pacli_neo, "RDI (categorical)" = RDI_pacli_neo_grp, therapy)) %>%
  tbl_summary(by = therapy,
              type = list(`RDI (continous)` ~ "continuous")) %>%
  bold_labels()
tbl6 <- Frontline %>% filter(dose_dense == 3) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("RDI (continous)" = RDI_pacli_adj, "RDI (categorical)" = RDI_pacli_adj_grp, therapy)) %>%
  tbl_summary(by = therapy,
              type = list(`RDI (continous)` ~ "continuous")) %>%
  bold_labels()

# tbl4 <- tbl_merge(list(tbl4_1, tbl4_2)) %>%
#   modify_spanning_header(everything() ~ NA_character_)
tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6),
          group_header = c(
                           "Carboplatin Neo", 
                           "Carboplatin Adj",
                           "Paclitaxel overall Neo",
                           "Paclitaxel overall Adj",
                           "Paclitaxel dose dense Neo",
                           "Paclitaxel dose dense Adj"),
          quiet = TRUE)
```

```{r Table summary Taxanes}
# tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c(RDI_carbo_neo, RDI_carbo_neo_grp, therapy)) %>%
#   tbl_summary(by = therapy) %>% 
#   bold_labels()
# 
# tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c(RDI_carbo_adj, RDI_carbo_adj_grp, therapy)) %>%
#   tbl_summary(by = therapy) %>%
#   bold_labels()
# tbl4 <- tbl_stack(list(tbl1, tbl2),
#           group_header = c(
#                            "paclitaxel Neo/Upfront Chemo",
#                            "paclitaxel Adj/Upfront Chemo"),
#           quiet = TRUE)
# 
# 
# tbl3 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c(RDI_carbo_adj, RDI_carbo_adj_grp, therapy)) %>%
#   tbl_summary(by = therapy) %>%
#   bold_labels()
# tbl_merge(list(tbl4, tbl3), tab_spanner = c("Overall", "Dose dense 1+3"))

@@

# tbl5 <- Frontline %>% filter(therapy == "Upfront Chemo" &
#                                dose_dense == 3) %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c("RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
#   tbl_summary() %>%
#   bold_labels()
# tbl6 <- Frontline %>% filter(therapy == "Upfront Surgery" &
#                                dose_dense == 3) %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c("RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
#   tbl_summary(
#               type = list(RDI ~ "continuous")) %>%
#   bold_labels()

# tbl8 <- tbl_merge(list(tbl2, tbl4))
# tbl9 <- tbl_merge(list(tbl3, tbl6), tab_spanner = c("Overall", "Dose dense 1+3"))

# tbl_stack(list(tbl1, tbl2, tbl3, tbl6),
#           group_header = c(
#                            "paclitaxel Neo/Upfront Chemo", 
#                            "paclitaxel Adj/Upfront Chemo",
#                            "paclitaxel Adj/Upfront Surgery",
#                            "dose dense paclitaxel Adj/Upfront Surgery"),
#           quiet = TRUE)
```
<br>

@@

## Univariable
```{r Table 5 HR}
# tbl2 <- Frontline %>%
#   filter(therapy == "Upfront Chemo")
# tbl1 <- tbl2 %>%
#   select(vitalstatus, RDI_carbo_neo, RDI_carbo_neo_grp) %>% 
#   tbl_uvregression(method = survival::coxph,
#                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>% 
#   add_
# tbl2 <- tbl2 %>%
#   select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
#   tbl_uvregression(method = survival::coxph,
#                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# 
# 
# tbl3 <- Frontline %>%
#   filter(therapy == "Upfront Surgery")
# tbl3 <- tbl3 %>%
#   select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
#   tbl_uvregression(method = survival::coxph,
#                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# tbl5 <- tbl_merge(list(tbl2, tbl3))
# 
# # tbl4 <- tbl_merge(list(tbl4_1, tbl4_2)) %>%
# #   modify_spanning_header(everything() ~ NA_character_)
# 
# tbl_stack(list(tbl1, tbl5)) %>%
#   bold_labels() %>%
#   italicize_levels()

  # trial %>%
  # select(age, grade, stage, trt) %>%
  # mutate(grade = paste("Grade", grade)) %>%
  # # tbl_strata(
  # #   strata = grade,
  # #   .tbl_fun =
  # #     ~ .x %>%
  #       tbl_summary(by = trt, missing = "no") %>%
  #       add_n()
  # )

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- tbl2 %>%
  select(vitalstatus, RDI_carbo_neo, RDI_carbo_neo_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- tbl2 %>%
  select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- tbl3 %>%
  select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- tbl2 %>%
  select(vitalstatus, RDI_pacli_neo, RDI_pacli_neo_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- tbl2 %>%
  select(vitalstatus, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- tbl3 %>%
  select(vitalstatus, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel/Upfront Chemo", 
                           "paclitaxel/Upfront Chemo",
                           "paclitaxel/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

@@

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_neo_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel Neo/Upfront Chemo", 
                           "paclitaxel Adj/Upfront Chemo",
                           "paclitaxel Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<!-- In multivariable analysis, categorical RDI for carboplatin or paclitaxel is not a factor associated with survival. -->

@@

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel Neo/Upfront Chemo", 
                           "paclitaxel Adj/Upfront Chemo",
                           "paclitaxel Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<!-- In multivariable analysis, a higher RDI for carboplatin shows a worse survival (p<0.001) in an Adjuvant / Upfront Chemo setting as seen in the univariable analysis.   -->
<!-- RDI for paclitaxel is not a factor associated with survival. -->

@@

## Adjusted by other drug
### RDI group
`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat` 
```{r Table 5 HR adjusted rdi group adjusted by other drug}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl2, tbl3),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<!-- When adjusting by each drugs, we observe a 61% increased risk of death for a underdosing of carboplatin in the Neoadjuvant / Upfront Chemo setting (p=0.059) and a 32% increased risk of death for a underdosing of paclitaxel in the Adjuvant / Upfront Surgery setting (p=0.059). -->

@@

<!-- # V.More precise RDI -->

<!-- As you saw, we have a big spread of RDI (it is more complicated than < or > 0.85) so I thought I could make more than 2 groups to compare patients who have a correct RDI, being underdosed or overdosed -->
